The role of standing variation in parallel adaptation

### 2014-09-22 standing-variation-paper.tex
.

We show that convergent adaptation within wide-spread species is likely to be
common, as has already been seen for a number of traits. 
On the basis of this we argue, in our discussion, that the genetics of
adaptation may often be
geographically local, and that we should expect to see relatively few
wide-spread sweeps even when selection pressures are wide-spread. 
We discuss some implications, and history, of this view for the evolutionary
coherence of species and molecular evolution.

@@

\paragraph{}
Our results are predicated on the idea that adaptive variants are
initially rare within populations, i.e.\ they are reasonably
deleterious before the environment switches. In constrast, even distant populations could have
a shared basis of adaptation if they adapt via common variation,
e.g.\ previously neutral (or nearly neutral) variation, shared among populations. 
Our ability to detect such shared convergent events is at the moment quite limited. 
If many loci contribute to variation in a trait, then
selection on any one allele may be weak, allowing adaptation to use different alleles in different populations.
However, in that case populations separated by a reasonable amount of drift may still
adapt via different genetic routes, as the constellation of alleles
best positioned to initially respond to positive selection, 
i.e.\ those at intermediate frequency, will be somewhat different. 
So it may be the case that polygenic traits are even less suspectible to a shared
genetic basis to adaptation across populations than simple traits.   
However, we currently lack models of this, and our ability to infer
such shared events means that empirically an answer for this question
may be limited for the moment.

>>>>

We show that convergent adaptation within wide-spread species is likely to be
common, as has already been seen for a number of traits. 
On the basis of this we argue, in our discussion, 
that the genetics of adaptation may often be geographically local, 
% and that we should expect to see relatively few wide-spread sweeps even when selection pressures are wide-spread. 
and that we should only expect to see widespread selective sweeps
when adaptation is highly constrained (e.g.\ by small mutation rate or having to cross a fitness valley).
We discuss some implications, and history, of this view for the evolutionary
coherence of species and molecular evolution.

@@

\paragraph{}
Our results are predicated on the idea that adaptive variants are
initially rare within populations, i.e.\ they are reasonably
deleterious before the environment switches. In constrast, even distant populations could have
a shared basis of adaptation if they adapt via common variation,
e.g.\ previously neutral (or nearly neutral) variation, shared among populations. 
Our ability to detect such shared convergent events is at the moment quite limited. 
If many loci contribute to variation in a trait, then
selection on any one allele may be weak, allowing adaptation to use different alleles in different populations.
However, in that case populations separated by a reasonable amount of drift may still
adapt via different genetic routes, as the constellation of alleles
at intermediate frequency will be somewhat different,
and these are the alleles that selection moves most quickly to change the trait value.
% best positioned to initially respond to positive selection, 
% i.e.\ those at intermediate frequency, will be somewhat different. 
So it may be the case that polygenic traits are even less suspectible to a shared
genetic basis to adaptation across populations than simple traits.   
However, we currently lack models of this, and our ability to infer
such shared events means that empirically an answer for this question
may be limited for the moment.
